### 2022-10-13 chapters/conclusion.tex
add : notes to be discussed in the future works

\begin{enumerate}
      \item ...
      \item ...
      \item ...

@@

\vfill \strut  % to fill the rest of the page with blank lines
\cleardoublepage

>>>>

\begin{enumerate}
      \item  vulgarisation of the energy consumption -> abstract numbers aren't enough 
      \item  Evolution of the energy consumption according to python version 
      \item Django vs Dlask vs Fast API, how do the ORMs affect the energy consumption while interacting with different web servers
      \item Deeper analysis for some web frameworks ( what is the reason behind an increase in power consumption while scaling ) 
      \item automation of the greenboard dashboard - the ability to run extra tests and add them to the dashboard 
      \item implementing multiple physical clients to techempower benchmarks platform - synchronisation problem - 
      \item a deeper analysis between the JVM optimizations and the JVM based programming languages 
      \item using github copilot ( codelabs) to compare the energy consumption of generated code -> extend the work of programming langauges 
      \item higher level progrmaming languges and the optimized target -> haxe -> java , check with other higher level lanagues 
      \item impact of LLVM on the energy consumption of the target language  compilation flags ..etc

@@

\subsection*{Representativeness} : 
What is the purpose of doing optimizations if they cannot be applied to real-world applications? 
\begin{enumerate}
      \item CI/CD energy tests  - joulediff - 
      \item Green commits 
      \item lazy code, sacrificing the performance in order to get a better energy consumption --> green faas 
      \item more representative benchmarks, using several CPU saturation levels 
      \item measuring the energy impact instead of the row energy consumption. ( the highway analogy when a single application consumes less energy, however the total energy consumption of the system increases )
\end{enumerate}
\vfill \strut  % to fill the rest of the page with blank lines
\cleardoublepage
